\documentclass{article}

% External references
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{IEEEtrantools}
\usepackage{mathrsfs}
\usepackage{longtable}

% Mathematical elements
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}
\newtheorem{lemma}{Lemma}
\newtheorem{observation}{Observation}
\newtheorem{proposition}{Proposition}
\theoremstyle{definition}\newtheorem{definition}{Definition}
\renewcommand{\IEEEproofindentspace}{0em}
\renewcommand{\IEEEQED}{\IEEEQEDopen}

\begin{document}
  \title{Gompertz Processes}
  \author{Aaron Geoffrey Sheldon}
  \date{\today}
  \maketitle
  \begin{abstract}
    Motivated by considering infinitesimal stochastic accelerations of time, we outline a
    theory of Gompertz processes, Poisson processes subordinated by integrated Geometric
    Brownian motion.
  \end{abstract}
  \section{Motivation}
  Integrated geometric Brownian motion occurs in the asymptotic limit of infinitesimal
  stochastic accelerations. In the context of accelerated failure times we are observing a
  fixed absorbing event. We do not have access to metabolic time, which integrated geometric
  Brownian motion models. By L\'evy-Khintchine this is the only representation that is
  L\'evy and jump free.
  \begin{definition}[Gompertz Process]
    A Gompertz process $G_t$ is a subordinated Poisson process $N_t$, with rate $\lambda$,
    where the subordinating process is integrated geometric Brownian motion $Y_t$, with
    drift $\mu$ and diffusion $\sigma$:
    \begin{IEEEeqnarray}{rCl}
      G_t
      & = & 
      N_{Y_t}
    \end{IEEEeqnarray}
    given:
    \begin{IEEEeqnarray}{rCl}
      Y_t
      & = & 
      \int_0^t X_s ds\\
      & = &
      \int_0^t e^{\mu s + \sigma W_s} ds
    \end{IEEEeqnarray}
  \end{definition}
  \section{Preliminaries}
  \begin{lemma}[Acceleration Lemma]
    Induction on powers of geometric Brownian motion, conditioned on integrated geometric
    Brownian motion.
  \end{lemma}
  \begin{lemma}[Recursion Convolution Lemma]
    Powers of integrated geometric Brownian motion.
  \end{lemma}
  \section{Martingale}
  Two point conditional expectation
  \section{L\'evy Process}
  Triangular matrix embedding resulting in independent multiplicative increments
  \section{Fokker-Planck}
  Two dimensional stochastic differential equation
  \section{Hazard Rate}
  Partial differential equation of Gompertz process hazard rate.
\end{document}